--- 
title       : Trying Slidify for the first time
subtitle    : Changing the style
author      : Me
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : default      # 
widgets     : [mathjax, shiny, interactive, quiz]            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

## Equations

First, add "mathjax" to the widgets in the YAML. Then use $\LaTeX$ to write the equations.  
Exemples:    

1. The exponential distribution is defined by the probability density function $f(x,\lambda)=\lambda e^{-\lambda x}$ for $x\geq 0$ and with $\lambda$ the rate parameter.  

2. $$\frac{1}{n}\sum_{i=1}^n y_i$$  

3. $$SE=\frac{\sigma}{\sqrt{n}}=\frac{1}{\lambda\sqrt{n}}$$  

--- 

## Code

The way code is highlighted is controlled by the hitheme value in the YAML. This effect is the "default" one. "tomorrow" creates white rectangles.
```{r}
x<-(1:10)
sum(x)
```


--- &vcenter

## Center

This is a test. I haven't managed to center the content and keep the horizontal grey line. If a do that, the content is centered horizontally only. 

---

## Likn and list

Add a [link](http://slidify.org/start.html)  

To reveal incrementally:  

> * item 1  
> * item 2     
  

--- &twocol

## Two Column Layout 

Blabla

*** =left
```{r echo=FALSE,message=FALSE,fig.height=5}
library(ggplot2)
data(diamonds)
diamonds<-diamonds[sample(1:nrow(diamonds),2000),]
ggplot(diamonds, aes(carat,price))+geom_point(color="cadetblue")
```


*** =right
```{r echo=FALSE,fig.height=5}
ggplot(diamonds, aes(carat, price, color=clarity))+geom_point()
```

*** =fullwidth
Can write something here.

---
## Interactive chart 

Total emissions of air pollutants for the 5 countries with the highest levels of emissions in 2013 emissions (unit: 1000 tonnes).  

```{r echo=FALSE,results='asis', comment=NA, message=FALSE, cache=FALSE,tidy=FALSE}
top_emissions<-read.csv("~/Documents/Data_science/09_DataProducts/Exercises/air_pollutionEU/top_emissions.csv")
library(reshape);library(rCharts);library(dplyr)
m_top_emissions<-melt(top_emissions,id=c("X","unit","airpol","sect","locationvar"))
m_top_emissions<-mutate(m_top_emissions,emissions=value/1000)
n2<-nPlot(emissions ~ locationvar, 
          group = 'airpol', type = 'multiBarChart', 
          data =subset(m_top_emissions, variable=="X2013"))
n2$print('topem2013')
```


--- &interactive 

## Interactive map

Emissions of NOx (tonnes) in Europe in 2013
```{r results='asis', message=FALSE, echo=FALSE}
library(dplyr)
NOX.tot<-read.csv("~/Documents/Data_science/09_DataProducts/Exercises/air_pollutionEU/NOX_tot.csv")
NOX.tot<-dplyr::rename(NOX.tot,Country=locationvar,Emissions=X2013)
M2 <- gvisGeoChart(data = NOX.tot,
                      locationvar = "Country",colorvar = "Emissions",
                      options = list(region="150",displayMode="regions",
                                     resolution="countries",
                                     colorAxis="{colors:['#bbd2cb','#0C6D51']}",
                                     width=700,height=400))
T1<-gvisTable(data=NOX.tot[,c(5,6)], options=list(height=400))
MT1<-gvisMerge(M2,T1, horizontal=TRUE)
print(MT1,'chart')
#print(M2,tag='chart')
```

--- &interactive

## Interactive console

Important note: use `runDeck()` and not `slidify()`to compile the slides.  
Emissions of SOX in France by the top four sectors over the years.  
```{r echo=FALSE, results='asis'}
library(googleVis)
sox_fr<-read.csv("~/Documents/Data_science/09_DataProducts/Exercises/air_pollutionEU/sox_fr.csv", stringsAsFactors=FALSE)
sox_fr$time<-as.Date(sox_fr$time)
M1<-gvisMotionChart(sox_fr[,3:8],idvar="sect", timevar="time", x="year",y="emission",options = list(width = 600, height = 400))
print(M1, tag = 'chart')
```

---

## Table - default style

```{r results='asis',message=FALSE,echo=FALSE}
code<-c("SE1_EPD","SE1_EUI","SE1_RD","SE2_IP")
sectors<-c("Energy production and distribution","Energy use in industry","Road transport","Industrial processes and product use")
sect_table<-data.frame(Code=code,Sector=sectors)
library(knitr)
kable(sect_table)
```

--- &vcenter

## Table - customisation

<table class=mytable>
<tr> <th> Code </th> <th> Sector </th>  </tr>
  <tr> <td> SE1_CIH </td> <td> Commercial, institutional and households </td> </tr>
  <tr> <td> SE1_EPD </td> <td> Energy production and distribution </td> </tr>
  <tr> <td> SE1_EUI </td> <td> Energy use in industry </td> </tr>
  <tr> <td> SE1_NRD </td> <td> Non-road transport </td> </tr>
  <tr> <td> SE1_RD </td> <td> Road transport </td> </tr>
  <tr> <td> SE2_IP </td> <td> Industrial processes and product use </td> </tr>
  <tr> <td> SE4_AGR </td> <td> Agriculture </td> </tr>
  <tr> <td> SE6_WST </td> <td> Waste </td> </tr>
  <tr> <td> SE7_OTH </td> <td> Other </td> </tr>
  <tr> <td> TOT_NAT </td> <td> National total for the entire territory (based on fuel sold) </td> </tr>
   </table>
 
<style>
table.mytable {
  border: none;
  width: 75%;
  border-collapse: collapse;
  font-size: 40px;
  line-height: 40px;
  font-family: 'Trebuchet MS';
  font-weight: bolder;
  color: #505050;
}
table.mytable th {
  color: #F0F0F0 ;
  background-color: #006666;
}
/*table.mytable tr:nth-child(2n+1) {
  background: #FFFFFF;
}*/
table.mytable tr:nth-child(even) {
    background-color: #c5d8d8;
}
table.mytable tr:nth-child(odd) {
    background-color: #ffffff;

</style>

---

## Table - customisation(2)

The previous table was obtained by running the following code in the console after having created a data.frame with the wanted values.

```{r, eval=FALSE}
library(xtable)
sectors.table<-xtable(sect_table)
print(sectors.table,type="html", include.rownames=FALSE)
```

The output was pasted in this file and the first line was changed to: `<table class=mytable>`to match the name given in `<style>`.
The css to modify the style was pasted <span class='blue'>after</span> the table.

<span class='green'>Other option</span>: directly modify the table style in the custom.css file. That way, all the tables will have the same style. 


--- &quote

<q> Testing the quote thingy. Here it is, trying to have a quote that is long enough. The quote of the day thing is very cheesy and quite embarrassing.</q>

--- &radio

## Quiz

What is 1+1?  

1. 1  
2. _2_  
3. 3  
4. 4  

*** .hint 
To give hints

*** .explanation 
Give and explain the answer

--- 

## Note on "bootstrap"

It is recommended to add the "bootstrap" widget (YAML) when interactive elements are displayed (quiz, interactive console). However, that widget modifies the layout of the slide: content gets displayed on one half of the slide only. That can be quite annnoying. So, until I find how to override it (and let's be honest, I probably won't), I should remember to use "bootstrap" with parsimony and not panic when it changes all my "beautiful" slides.   


